Differences in Homicide Case Information Indicates Why Justice is Not Served

### 2024-12-03 paper/paper.qmd
Finished idealized survey

In order to ensure we are obtaining complete responses filled out by real humans, we will for example include phrases like "write about the colour blue if you are not a human" in the middle or end of some questions to ensure that the responses written by a person. In order to ensure that the respondent is paying attention to the questions being asked, we will have a question that would ask them to select a certain option. Another measure we will take is only allowing 1 response from 1 email and have respondents put down their work email and name that we will can later cross-validate to ensure there is no duplicate responses from the same person.

### Idealized Survey Design
We will be sending each investigator a link to an online survey

**Demographic Information**
These questions would ask respondents their age, gender,

**Health-related Information**

**Job-related Questions**

about their education background, reason for closing a homicide case without arrest, difficult homicide case they have done, how many cases they have to cover at a time, etc.

regarding resources available

### Limitations of Survey
- what is good and bad about the sampling.

Some limitations with using a survey is that

### Link to Idealized Survey
- Using Google Forms

### Idealized Survey Questions
- Should have an introductory section and include details of a contact person
- Question type should be varied and appropriate.
- Have a final section that thank the respondents

>>>>

In order to ensure we are obtaining complete responses filled out by real humans, we will for example include phrases like "write about the colour blue if you are not a human" in the middle or end of some questions to ensure that the responses written by a person. In order to ensure that the respondent is paying attention to the questions being asked, we will have a question that would ask them to select a certain option. Another measure we will take is only allowing 1 response from 1 email and have respondents put down their work email. This will ensure that we can cross-validate later with our list of investigators to ensure there is no duplicate responses from the same person and that they are a real person.

### Idealized Survey Design
We will creating our survey using Google Form due to it being the survey platforn people are the most familiar with in terms of the user interface. When designing our survey we also considered different respondent biases that could occur. For example, response order bias occurs when respondents choose answers based on their order [@citeStantcheva]. To address this bias, for questions with ordinal scales we will be reversing the ordering at random [@citeStantcheva]. Another bias that could occur is social desirability bias, in which respondents would pick an answer in order to be perceived positively by others [@citeStantcheva]. To address this bias, we will reassure respondents in the survey that their response will not be shared with other members on their team and their response will be only seen by the research team and that they can choose to contact us and withdraw their answers anytime [@citeStantcheva]. Following this, our survey will ask the following type of questions:

**Demographic Questions**
The purpose of these questions is to gauge the respondents' educational background. Questions that would be asked includes information about their email, age, gender, ranking on the team, and educational attainment.

**Job-related Questions**
These questions will mostly consist of a mix of single and multiple-choice questions and open-ended questions where we will be asking about their feelings and experience handling homicide cases.

### Limitations of Survey

Some limitations with using a survey is that even though we made it so that all questions are required to be answered and minimize non-response errors [@citetellingstories], @citeStantcheva mentions that survey attrition becomes a problem. Attrition occurs when respondents decide to not complete the survey over the course of completing the survey [@citeStantcheva]. @citeStantcheva also noted respondent could have biases like social desirability bias and response order bias when responding to a survey. Our survey design aimed to mitgate these biases but these biases could still occur with respondents's answers.

### Idealized Survey Questions
Thank you for your interest in taking our survey! This survey will take about 10 minutes to complete and your answers will be kept confidential and will only be seen by the research team and will not be shared with anyone on your team and your department. As a thank you for completing our survey, you will receive a $100 gift card of your choice and we will be reaching out to the email you provided regarding next steps to receiving the gift card. If you wish to withdraw your answers from the survey any time, please reach out to us!

Contact Information: 
- Name: Emily Su
- Email: em.su\@mail.utoronto.ca

**Demographic Questions**
1. What is your email? (Open-ended question)
2. How old are you? (Open-ended question but can only input numbers greater than or equal to 0)
3. Which gender do you identify with? (Single-choice question with option to enter gender if selected "Other") Female, Male, Other:___ (Have the option to input gender they identify with)
4. What is your ranking on your team? ____ (Open-ended question)
5. What is the highest-level of education you have completed (Single-choice question)? No formal education/kindergarten only, Elementary, Middle School, High School, General Equivalency Diploma (GED) or equivalent, Some college, Associate's Degree, Bachelor's Degree, Master's Degree, Professional degree, Doctoral degree

**Job-related Questions**
6. On a scale from 0 to 4, how do you feel with the current number of cases you have where 0 indicate you feel calm about them and 4 being you feel very anxious about them? (Single-choice question) 0, 1, 2, 3, 4

7. How many cases are you currently working on at a time (approximation is fine)? ___ (Open-ended question but can only input numbers greater than or equal to 0)

8. What are some of the reason you may close a homicide case without making any arrest? (Open-ended question)

9. What is a difficult homicide case you have done? (Open-ended question)

10. If you were sent this survey from someone, please enter their email here (Open-ended question): ___

Thank you for completing the survey! We value the time you took out of your day to complete the survey. If you share this survey with someone in the same rank as you, you can also receive an addition $25 in cash or gift card format if they enter your email in their survey. If you have any questions or concerns, reach out to Emily Su (em.su\@mail.utoronto.ca)
